A Proposed Translation of B Implementations to the LLVM

### 2013-07-19 PAPERS/2013-SBMF/paper_short.tex
no message

\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{amssymb}
\usepackage[fleqn]{amsmath}
\usepackage[colorlinks=true]{hyperref}
\usepackage{xspace,framed,here,keystroke}
\pagestyle{headings}
\title{A Proposed of Translation of B Implementations to the LLVM}
\author{David D\'{e}harbe \inst{1} \and Val\'{e}rio Medeiros Jr.\inst{2}}
\institute{Federal University of Rio Grande do Norte, UFRN, Brazil\\
\and 
Federal Institute of Education, Science and Technology  of Rio Grande do Norte, IFRN, Brazil}
\date{May 2013}

@@

  \end{minipage}
  \caption{Simple example of a B function and its corresponding  C function and LLVM function.
    It is not a real translation, but it help to understand the translation %TODO to update the variables
    The first line contains the signature: return type \llvm{void}, the name
    \llvm{@inc} and one parameter named \llvm{\%pi} and typed \llvm{i32*}.  Next
    is the body with a single block, labeled \llvm{entry}, and temporary
    variables \llvm{\%0} and \llvm{\%1}, created in the conversion to SSA. The
    block has four instructions: \llvm{load}, \llvm{add}, \llvm{store} and
    \llvm{ret}. For instance, \llvm{\%1 = add i32 \%0, 1} is an addition
    (\llvm{add}), has result type \llvm{i32} and assigns to
    \llvm{\%1} the sum of variable \llvm{\%0} and integer
    literal \llvm{1}.}
  \label{fig:ex-llvm}
\end{figure}

>>>>

\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{amssymb}
\usepackage[fleqn]{amsmath}
\usepackage[colorlinks=true]{hyperref}
\usepackage{xspace,framed,here,keystroke}
\pagestyle{headings}
\title{A Proposed Translation of B Implementations to the LLVM}
\author{David D\'{e}harbe \inst{1} \and Val\'{e}rio Medeiros Jr.\inst{2}}
\institute{Federal University of Rio Grande do Norte, UFRN, Brazil\\
\and 
Federal Institute of Education, Science and Technology  of Rio Grande do Norte, IFRN, Brazil}
\date{May 2013}

@@

  \end{minipage}
  \caption{Simple example of a B function and its corresponding  C function and LLVM function.
    It is not a real translation, but it helps to understand the translation. %TODO to update the variables
    The first line contains the signature: return type \llvm{void}, the name
    \llvm{@inc} and one parameter named \llvm{\%pi} and typed \llvm{i32*}.  Next
    is the body with a single block, labeled \llvm{entry}, and temporary
    variables \llvm{\%0} and \llvm{\%1}, created in the conversion to SSA. The
    block has four instructions: \llvm{load}, \llvm{add}, \llvm{store} and
    \llvm{ret}. For instance, \llvm{\%1 = add i32 \%0, 1} is an addition
    (\llvm{add}), has result type \llvm{i32} and assigns to
    \llvm{\%1} the sum of variable \llvm{\%0} and integer
    literal \llvm{1}.}
  \label{fig:ex-llvm}
\end{figure}
